Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-11 analysis/paper/paper.Rmd
Add effect size objects

load(system.file("extdata",
            "m_f1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_f2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_g1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_g2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_h1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_h2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_i1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_i2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
```

>>>>

load(system.file("extdata",
                 "m_f1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f1_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f2_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_g1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g1_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g2_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_h1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h1_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_i1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i1_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_i2_effectsize.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
```
